Analysing Melbourne CBD pedestrian counts data with a focus on imputation methods

### 2017-10-22 thesis_draft/01-chap1.Rmd
need to fix references, add more lit review, longer intro, longer conclusion, longer motivation, add acknowledgements

#Background

@@

No sensor location has complete data for the period between between 1/1/2014 and `r paste(day(today()), month(today()), year(today()), sep = "/")`.

# Literature Review
<!-- #### IMPUTATION OF MISSING CLASSIFIED TRAFFIC DATA DURING WINTER SEASON - _Hyuk-Jae Roh, Satish Sharma, Prasanta K. Sahu_   -->

@@

```{r, fig.cap = paste("A plot of the in-sample Actual vs Predicted pedestrian counts at Australia on Collins (sensor location with large proportion of missing values) for the simple GLM model and the improved GLM model. The dashed line is $x=y$, representing a reference for perfect fit, while solid line is the linear fit of the points. The improvement in the imputation model is significant, where the predicted values lie closer to the dashed line. The simple model shows bias caused by the false zero-counts, causing underestimation. ")}

>>>>

# Background

@@

The period of data which is being used for analysis is between 01/01/2014 to 22/10/2017 (date of this paper). This is due to the poor quality of the dataset pre-2014 with many missing values with few sensors being installed during at the start of pedestrian counts recording (in 2009).

Even with a truncated period for the data, no sensor location has complete data for the period between between 01/01/2014 and 31/12/2016 (the training period to be used for predictive models in the paper). As a result, imputation of the data is required for meaningful analysis of pedestrian behaviour.

### Literature Review
<!-- #### IMPUTATION OF MISSING CLASSIFIED TRAFFIC DATA DURING WINTER SEASON - _Hyuk-Jae Roh, Satish Sharma, Prasanta K. Sahu_   -->

@@

```{r, fig.cap = paste("A plot of the in-sample Actual vs Predicted pedestrian counts at Australia on Collins (sensor location with large proportion of missing values) for the simple GLM model and the improved GLM model. The dashed line is $x=y$, representing a reference for perfect fit, while solid line is the linear fit of the points. The improvement in the imputation model is significant, where the predicted values lie closer to the dashed line. The simple model shows bias caused by the false zero-counts, causing underestimation.")}
